Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-14 response_to_reviewers.tex

\begin{quote}
\color{blue}
We replaced the words according to the reviewer's suggestion:
\end{quote}

\textbf{29. Reviewer's Comment:}
Page 9, Conclusions section, sentence beginning “Moreover, some of these
splits...”: replace “splits” with “shifts”.

\textbf{29. Response:}
\begin{quote}
\color{blue}
We replaced the word according to the reviewer's suggestion:
\end{quote}

\textbf{30. Reviewer's Comment:}
Page 10, sentence beginning “We recommend that all datasets...”: why are the
authors recommending using MEDUSA at all, as opposed to MultiMEDUSA?

\textbf{30. Response:}
\begin{quote}
\color{blue}
We reworded the sentence and now we recommend using MultiMEDUSA.
\end{quote}

\textbf{31. Reviewer's Comment:}
Page 10, second full paragraph: the results described here (rate increase in 
Ithomiini \& Charaxes, rate decrease in Danaina) are incongruent with those
described on page six (four rate increases). This incongruence needs to be 
addressed.

\textbf{31. Response:}
\begin{quote}
\color{blue}
We revised the paragraph and included the two other increases
in diversification rate: \emph{Ypthima} and the clade \emph{Callicore} + 
\emph{Diaethria}
\end{quote}

### 2015-01-14 MS_revised.tex
comment 31

Our MultiMEDUSA approach to perform analyses on the posterior
distribution of trees found strong support for an increase in net
diversification rate in the tribe Ithomiini and the genus
\emph{Charaxes}, and for a decrease in net diversification rate in the
subtribe Danaina. Due to phylogenetic uncertainty, we did not obtain
strong support for other diversification shifts in Nymphalidae. Our
BiSSE analysis corroborated other studies in that the trait ``feeding on
Solanaceae'', or a codistributed character, was important in the
diversification of Ithomiini butterflies. However, by applying MEDUSA we
found that a critical character in the radiation of the group might have
appeared after the shift from Apocynaceae to Solanaceae. We also found
that the trait ``feeding on Apocynaceae'' is not responsible for the
slowdown of diversification in Danaina. Ithomiini and Solanaceae
diversified near simultaneously, which is in agreement with the diffuse
cospeciation hypothesis \cite{nyman2012, janz2011}.

\section*{Acknowledgments}
We are thankful to Mark Cornwall for help with the script to extend
MEDUSA to include phylogenetic uncertainty, Niklas Wahlberg for
commenting on the manuscript and giving us the posterior distribution of
trees, Luke Harmon for commenting on the manuscript and anonymous
reviewers for their comments, which greatly improved the manuscript,
Jessica Slove Davidson and Niklas Janz for access to their hostplant
data. The study was supported by a Kone Foundation grant (awarded to
Niklas Wahlberg), Finland (C. Pe\~na) and the Research Council of Norway
(grant no. 204308 to M. Espeland). We acknowledge CSC--IT Center for
Science Ltd. (Finland) for the allocation of computational resources.

>>>>

Our MultiMEDUSA approach to perform analyses on the posterior
distribution of trees found strong support for an increase in net
diversification rate in the tribe Ithomiini, the genera \emph{Ypthima},
\emph{Charaxes}, the clade \emph{Callicore} + \emph{Diaethria} and for a
decrease in net diversification rate in the
subtribe Danaina. Due to phylogenetic uncertainty, we did not obtain
strong support for other diversification shifts in Nymphalidae. Our
BiSSE analysis corroborated other studies in that the trait ``feeding on
Solanaceae'', or a codistributed character, was important in the
diversification of Ithomiini butterflies. However, by applying MEDUSA we
found that a critical character in the radiation of the group might have
appeared after the shift from Apocynaceae to Solanaceae. We also found
that the trait ``feeding on Apocynaceae'' is not responsible for the
slowdown of diversification in Danaina. Ithomiini and Solanaceae
diversified near simultaneously, which is in agreement with the diffuse
cospeciation hypothesis \cite{nyman2012, janz2011}.

\section*{Acknowledgments}
We are thankful to Mark Cornwall for help with the script to extend
MEDUSA to include phylogenetic uncertainty, Niklas Wahlberg for
commenting on the manuscript and giving us the posterior distribution of
trees, Luke Harmon for commenting on the manuscript, Jeffrey C. Oliver and anonymous
reviewers for their comments, which greatly improved the manuscript,
Jessica Slove Davidson and Niklas Janz for access to their hostplant
data. The study was supported by a Kone Foundation grant (awarded to
Niklas Wahlberg), Finland (C. Pe\~na) and the Research Council of Norway
(grant no. 204308 to M. Espeland). We acknowledge CSC--IT Center for
Science Ltd. (Finland) for the allocation of computational resources.
